---
title: "RStudio_VehicleFleetStatus"
output: html_document
---

```{r setup, include=FALSE}
options(knitr.table.format = "html")
library(tidyverse)
library(purrr)
library(ggplot2)
library(dplyr)
library(RODBC)
library(kableExtra)
library(lubridate)

db <- "C:/Users/J305843/Documents/R_Projects/VehicleFleetStatus.accdb"
con <- odbcConnectAccess2007(db)
Fleet <- sqlFetch(con,"FleetStatus")
```

## Data Grabbing

The code filters the access file to grab what we need and formats them based on the vehicle model

For some of the plots, they need to be plotted with respect to time. It is needed to change the dates to obtainable values

```{r modifications and stats}
md1 <- Fleet %>%
      select(ID,Vehicle,Status,"Start Date", "End Date")
md1$Vehicle <- as.factor(md1$Vehicle)



end_date <- as.Date(md1$`End Date`, format="%d-%m-%Y")
start_date <- as.Date(md1$`Start Date`, format="%d-%m-%Y")

md1 <- mutate(md1, num_days=end_date - start_date)

md1 <- md1 %>% 
        mutate_if(is.factor, as.character)

Dodge <- md1 %>% filter(Vehicle == "Dodge")

make_plot <- function(dataset, type){
        ggplot(dataset)+
        geom_segment(aes(x = `Start Date`, xend = `End Date`, y = Status, yend = Status, size=10, colour=Status))+
        theme_minimal()+
        scale_color_manual(values=c('dark green','red','yellow'))+
        labs(y='Status of Vehicle', x='Time of Status', shape='Status Color')+
        ggtitle(paste0(type," Status in 2020"))+
        theme(plot.title=element_text(hjust=.5), panel.grid=element_line(color='black'),
              panel.background=element_rect(fill='white'))
  
}



```

## Plots

The first plot is a bar plot with the different tickets of each model

```{r plotting, echo = TRUE}
plt1 <- ggplot(md1, aes(Vehicle, fill=Status))+
        geom_bar(color="black")+
        theme_minimal()+
        scale_fill_manual(values=c('green','red','yellow'))+
        labs(y='Number of Vehicle with Status', x='Vehicle Model', shape='Status Color')+
        ggtitle("Overall Vehicle Status")+
        theme(plot.title=element_text(hjust=.5), panel.grid=element_line(color='black'),
              panel.background=element_rect(fill='papayawhip'))

print(plt1)

vehicle_results <- md1 %>%
  group_by(Vehicle) %>%
  nest() %>%
  mutate(plots = map2(.x = data,
                      .y = Vehicle,
                      ~make_plot(dataset = .x, type = .y)))

plt2 <- ggplot(Dodge)+
        geom_segment(aes(x = `Start Date`, xend = `End Date`, y = Status, yend = Status, size=10, colour=Status))+
        theme_minimal()+
        scale_color_manual(values=c('dark green','red','yellow'))+
        labs(y='Status of Vehicle', x='Time of Status', shape='Status Color')+
        ggtitle("Dodge Status in 2020")+
        theme(plot.title=element_text(hjust=.5), panel.grid=element_line(color='black'),
              panel.background=element_rect(fill='white'))
        
print(plt2)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
